---
title: "coursera_multiple_regression"
author: "Andrew Sinkevich"
date: "10 01 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
header-includes:
- \usepackage{amssymb,amsmath}
 

- \usepackage[utf8]{inputenc}

- \usepackage{graphicx}
- \setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
---

```{r, echo=FALSE}
library(readxl)
library(rmarkdown)
TestExer2_GPA <- read_excel("~/done/TestExer2-GPA-round2.xls")
attach(TestExer2_GPA)

```
```{r}
#devtools::install_github("rstudio/rmarkdown")
```


(a)

i)
```{r}
lm.fit<-lm(FGPA~SATV)
summary(lm.fit)
```
***Answer:*** the coefficient of SATV is 0.06, it's standart error and p-value are 0.02766 and 0.0229 respectively.


ii)
***confidence interval for beta***
```{r}
0.06309+ qnorm(0.95)*0.02766 
0.06309- qnorm(0.95)*0.02766 
```

***Answer:*** 95% confidence interval for $\beta$ lies from 0.017 to 0.108   

(b)
i)
```{r}
lm.fit.full<-lm(FGPA~ SATM+SATV+FEM)
summary(lm.fit.full)
```

ii)
```{r}

0.014+qnorm(0.95)*0.027
0.014-qnorm(0.95)*0.027
```

***Answer:***in the second regression $FGPA = SATM+SATV+FEM$,  the 95% confidence interval of $\beta$ lies from -0.03041105 to 0.05841105


(c)

***Correlation matrix***
```{r,echo=FALSE}
library(dplyr)
library(pander)
TestExer2_GPA<-select(TestExer2_GPA,-Observation)
correlationMatrix <-cor(TestExer2_GPA)
pander::pandoc.table(correlationMatrix, caption="correlation matrix",split.cells = 1, split.tables=100,style = c("rmarkdown"), emphasize.strong.cells=which(correlationMatrix> 0.5, arr.ind = TRUE))

```

(d)

```{r, echo=FALSE}
Ftest.lm <- function(reg0,reg1)
	{
	N <- nrow(reg0$model)
	n <- ncol(reg0$model)-1
	k <- ncol(reg0$model) - ncol(reg1$model)

	ssr0 <- sum(residuals(reg0)^2)
	ssr1 <- sum(residuals(reg1)^2)	

	F  <- (ssr1-ssr0)/ssr0*(N-n)/k
	PF <- 1 - pf(F, k, N-n)

	list("F-stat"=F, "P-value"=PF)
}
```

```{r}
Ftest.lm(lm.fit.full, lm.fit)

```

***Answer:***
F-test is equal to 24.6058, so we have all reasons to accept H1 (we reject a H0 hypothesis of indentical influence of  $SATM+SATV+FEM$ and $SATM$ on the regression).

#



